\documentclass[a4paper,12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\usepackage{times}

\begin{document}

\section*{Mathematical Description of Linear Regression}

Linear regression is a statistical method used to model the relationship between a dependent variable $y$ and one or more independent variables $\mathbf{x}$. It assumes a linear relationship between the variables and seeks to find the best-fitting line that minimizes prediction errors. Below is the mathematical formulation.

\subsection*{1. Model Representation}
For a dataset with $n$ features, the dependent variable $y \in \mathbb{R}$ is modeled as a linear combination of the feature vector $\mathbf{x} \in \mathbb{R}^n$:

\[
y = \mathbf{w}^T \mathbf{x} + b + \epsilon
\]

\begin{itemize}
    \item $\mathbf{w} \in \mathbb{R}^n$: Weight vector, representing the coefficients of the features.
    \item $b \in \mathbb{R}$: Bias term (intercept).
    \item $\mathbf{w}^T \mathbf{x} + b$: Predicted value, denoted as $\hat{y}$.
    \item $\epsilon$: Random error term, assumed to be normally distributed with mean 0 and variance $\sigma^2$.
\end{itemize}

For a dataset with $m$ samples $\{ (\mathbf{x}^{(i)}, y^{(i)}) \}_{i=1}^m$, the prediction for the $i$-th sample is:

\[
\hat{y}^{(i)} = \mathbf{w}^T \mathbf{x}^{(i)} + b
\]

\subsection*{2. Objective Function}
The goal is to find the parameters $\mathbf{w}$ and $b$ that minimize the prediction error. The \textbf{Mean Squared Error (MSE)} is commonly used as the loss function:

\[
J(\mathbf{w}, b) = \frac{1}{m} \sum_{i=1}^m (y^{(i)} - \hat{y}^{(i)})^2 = \frac{1}{m} \sum_{i=1}^m (y^{(i)} - (\mathbf{w}^T \mathbf{x}^{(i)} + b))^2
\]

The objective is to minimize $J(\mathbf{w}, b)$ with respect to $\mathbf{w}$ and $b$.

\subsection*{3. Optimization}
The loss function $J(\mathbf{w}, b)$ is convex, allowing optimization through \textbf{closed-form solutions} or \textbf{iterative methods} such as gradient descent.

\subsubsection*{3.1 Closed-Form Solution}
Linear regression allows the optimal parameters to be derived analytically using the \textbf{normal equation}. Let $\mathbf{X} \in \mathbb{R}^{m \times (n+1)}$ be the design matrix, where each row is $[\mathbf{x}^{(i)}, 1]$ (appending a 1 for the bias term), and $\mathbf{y} \in \mathbb{R}^m$ the vector of target values. The parameters $\boldsymbol{\theta} = [\mathbf{w}, b]$ are computed as:

\[
\boldsymbol{\theta} = (\mathbf{X}^T \mathbf{X})^{-1} \mathbf{X}^T \mathbf{y}
\]

This solution assumes that $\mathbf{X}^T \mathbf{X}$ is invertible, requiring that the features are not perfectly collinear and $m \geq n+1$.

\subsubsection*{3.2 Gradient Descent}
Alternatively, gradient descent iteratively updates the parameters to minimize the loss. The gradients of the loss function are:

\[
\frac{\partial J}{\partial \mathbf{w}} = \frac{2}{m} \sum_{i=1}^m (\hat{y}^{(i)} - y^{(i)}) \mathbf{x}^{(i)}
\]

\[
\frac{\partial J}{\partial b} = \frac{2}{m} \sum_{i=1}^m (\hat{y}^{(i)} - y^{(i)})
\]

The parameters are updated as:

\[
\mathbf{w} \leftarrow \mathbf{w} - \alpha \frac{\partial J}{\partial \mathbf{w}}, \quad b \leftarrow b - \alpha \frac{\partial J}{\partial b}
\]

where $\alpha$ is the learning rate.

\subsection*{4. Regularization}
To prevent overfitting, especially when $n$ is large or features are correlated, regularization can be applied. Common approaches include:

\begin{itemize}
    \item \textbf{L2 Regularization (Ridge Regression)}: Adds a penalty on the magnitude of the weights to the loss function:

    \[
    J(\mathbf{w}, b) = \frac{1}{m} \sum_{i=1}^m (y^{(i)} - (\mathbf{w}^T \mathbf{x}^{(i)} + b))^2 + \lambda \| \mathbf{w} \|^2
    \]

    \begin{itemize}
        \item $\lambda$: Regularization parameter.
    \end{itemize}

    The normal equation for Ridge Regression is:

    \[
    \boldsymbol{\theta} = (\mathbf{X}^T \mathbf{X} + \lambda \mathbf{I})^{-1} \mathbf{X}^T \mathbf{y}
    \]

    where $\mathbf{I}$ is the identity matrix (excluding the bias term from regularization).

    \item \textbf{L1 Regularization (Lasso Regression)}: Adds a penalty on the absolute values of the weights:

    \[
    J(\mathbf{w}, b) = \frac{1}{m} \sum_{i=1}^m (y^{(i)} - (\mathbf{w}^T \mathbf{x}^{(i)} + b))^2 + \lambda \| \mathbf{w} \|_1
    \]

    Lasso encourages sparsity, setting some weights to zero, but typically requires iterative optimization.
\end{itemize}

\subsection*{5. Assumptions}
Linear regression assumes:
\begin{itemize}
    \item Linearity: The relationship between $\mathbf{x}$ and $y$ is linear.
    \item Independence: Observations are independent.
    \item Homoscedasticity: Constant variance of errors.
    \item Normality: Errors are normally distributed (for inference purposes).
    \item No multicollinearity: Features are not perfectly collinear.
\end{itemize}

\subsection*{6. Evaluation}
The model’s performance is commonly evaluated using metrics such as:
\begin{itemize}
    \item \textbf{Mean Squared Error (MSE)}: As defined above.
    \item \textbf{Root Mean Squared Error (RMSE)}: $\sqrt{\text{MSE}}$.
    \item \textbf{$R^2$}: Proportion of variance in $y$ explained by the model:

    \[
    R^2 = 1 - \frac{\sum_{i=1}^m (y^{(i)} - \hat{y}^{(i)})^2}{\sum_{i=1}^m (y^{(i)} - \bar{y})^2}
    \]

    where $\bar{y}$ is the mean of the target values.
\end{itemize}

\subsection*{7. Summary}
Linear regression models the relationship between features and a continuous outcome using a linear function, optimized by minimizing the mean squared error. It can be solved analytically or via gradient descent, with regularization to improve generalization. The model is simple, interpretable, and widely used for predictive tasks.

\end{document}1.6swrite a mathematical description about logistic regression in latexLogistic_Regression.texlatex2.4sInterruptedin english pleaselatex\documentclass[a4paper,12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\usepackage{times}

\begin{document}

\section*{Mathematical Description of Logistic Regression}

Logistic regression is a statistical model used for binary classification, extendable to multiclass problems via techniques like softmax regression. It predicts the probability that a given input belongs to a particular class. Below is the mathematical formulation.

\subsection*{1. Model Representation}
For a binary classification problem, the goal is to predict the probability $P(y=1 | \mathbf{x})$, where $y \in \{0, 1\}$ is the class label, and $\mathbf{x} \in \mathbb{R}^n$ is the feature vector. The logistic regression model assumes this probability follows the logistic (sigmoid) function:

\[
P(y=1 | \mathbf{x}) = \sigma(\mathbf{w}^T \mathbf{x} + b) = \frac{1}{1 + e^{-(\mathbf{w}^T \mathbf{x} + b)}}
\]

\begin{itemize}
    \item $\mathbf{w} \in \mathbb{R}^n$: Weight vector (parameters to be learned).
    \item $b \in \mathbb{R}$: Bias term (intercept).
    \item $\mathbf{w}^T \mathbf{x} + b$: Linear combination of features, often denoted as $z$.
    \item $\sigma(z) = \frac{1}{1 + e^{-z}}$: Sigmoid function, mapping $z \in \mathbb{R}$ to $[0, 1]$.
\end{itemize}

The probability of the negative class is:

\[
P(y=0 | \mathbf{x}) = 1 - P(y=1 | \mathbf{x}) = \frac{e^{-(\mathbf{w}^T \mathbf{x} + b)}}{1 + e^{-(\mathbf{w}^T \mathbf{x} + b)}}.
\]

\subsection*{2. Decision Rule}
To classify an input $\mathbf{x}$, a threshold (typically 0.5) is applied to the predicted probability:

\[
\hat{y} =
\begin{cases} 
1 & \text{if } P(y=1 | \mathbf{x}) \geq 0.5 \\
0 & \text{otherwise}
\end{cases}
\]

Since $P(y=1 | \mathbf{x}) = \sigma(z)$, and $\sigma(z) = 0.5$ when $z = 0$, this is equivalent to:

\[
\hat{y} =
\begin{cases} 
1 & \text{if } \mathbf{w}^T \mathbf{x} + b \geq 0 \\
0 & \text{otherwise}
\end{cases}
\]

\subsection*{3. Loss Function}
The parameters $\mathbf{w}$ and $b$ are learned by minimizing the \textbf{log-loss} (or \textbf{binary cross-entropy loss}). For a dataset of $m$ samples $\{ (\mathbf{x}^{(i)}, y^{(i)}) \}_{i=1}^m$, the log-loss is:

\[
J(\mathbf{w}, b) = -\frac{1}{m} \sum_{i=1}^m \left[ y^{(i)} \log(P(y=1 | \mathbf{x}^{(i)})) + (1 - y^{(i)}) \log(1 - P(y=1 | \mathbf{x}^{(i)})) \right]
\]

Substituting $P(y=1 | \mathbf{x}^{(i)}) = \sigma(\mathbf{w}^T \mathbf{x}^{(i)} + b)$, the loss becomes:

\[
J(\mathbf{w}, b) = -\frac{1}{m} \sum_{i=1}^m \left[ y^{(i)} \log(\sigma(\mathbf{w}^T \mathbf{x}^{(i)} + b)) + (1 - y^{(i)}) \log(1 - \sigma(\mathbf{w}^T \mathbf{x}^{(i)} + b)) \right]
\]

\subsection*{4. Optimization}
The loss function $J(\mathbf{w}, b)$ is convex, so optimization techniques like \textbf{gradient descent} are used to find the optimal parameters. The gradients with respect to $\mathbf{w}$ and $b$ are:

\[
\frac{\partial J}{\partial \mathbf{w}} = \frac{1}{m} \sum_{i=1}^m \left( \sigma(\mathbf{w}^T \mathbf{x}^{(i)} + b) - y^{(i)} \right) \mathbf{x}^{(i)}
\]

\[
\frac{\partial J}{\partial b} = \frac{1}{m} \sum_{i=1}^m \left( \sigma(\mathbf{w}^T \mathbf{x}^{(i)} + b) - y^{(i)} \right)
\]

In gradient descent, the parameters are updated iteratively:

\[
\mathbf{w} \leftarrow \mathbf{w} - \alpha \frac{\partial J}{\partial \mathbf{w}}, \quad b \leftarrow b - \alpha \frac{\partial J}{\partial b}
\]

where $\alpha$ is the learning rate.

\subsection*{5. Regularization (Optional)}
To prevent overfitting, regularization terms (e.g., L2 or L1) can be added to the loss function. For \textbf{L2 regularization}, the loss becomes:

\[
J(\mathbf{w}, b) = -\frac{1}{m} \sum_{i=1}^m \left[ y^{(i)} \log(\sigma(\mathbf{w}^T \mathbf{x}^{(i)} + b)) + (1 - y^{(i)}) \log(1 - \sigma(\mathbf{w}^T \mathbf{x}^{(i)} + b)) \right] + \frac{\lambda}{2} \| \mathbf{w} \|^2
\]

\begin{itemize}
    \item $\lambda$: Regularization parameter controlling the strength of the penalty.
    \item $\| \mathbf{w} \|^2$: L2 norm of the weights (encourages smaller weights).
\end{itemize}

The gradient for $\mathbf{w}$ is modified to include the regularization term:

\[
\frac{\partial J}{\partial \mathbf{w}} = \frac{1}{m} \sum_{i=1}^m \left( \sigma(\mathbf{w}^T \mathbf{x}^{(i)} + b) - y^{(i)} \right) \mathbf{x}^{(i)} + \lambda \mathbf{w}
\]

\subsection*{6. Multiclass Extension (Softmax Regression)}
For $K$-class classification, logistic regression is generalized to \textbf{softmax regression}. The model outputs probabilities for each class using the softmax function:

\[
P(y=k | \mathbf{x}) = \frac{e^{\mathbf{w}_k^T \mathbf{x} + b_k}}{\sum_{j=1}^K e^{\mathbf{w}_j^T \mathbf{x} + b_j}}
\]

\begin{itemize}
    \item $\mathbf{w}_k, b_k$: Parameters for class $k$.
\end{itemize}

The loss function is the \textbf{categorical cross-entropy}, and optimization proceeds similarly.

\subsection*{7. Summary}
Logistic regression models the probability of a binary outcome using the sigmoid function, optimizing parameters via gradient descent on the log-loss. Regularization can be applied to improve generalization. The model is interpretable, computationally efficient, and widely used for binary classification tasks.

\end{document}2swrite mathematical description in latex in english about random forestRandom_Forest.texlatex•2.7sHow can Grok help?